\begin{recipe}
[% 
    preparationtime = {\unit[45]{m}},
    bakingtime={\unit[6-8]{h}},
    portion = {\portion{5-6}},
    source = {chowhound.com, author is listed as Christine Gallary}
]
{Easy Slow Cooker Chili}
    
    \graph
    {% pictures
        small=pic/glass,     % small picture
        big=pic/ingredients  % big picture
    }
    
    \introduction{%
        So this is the chili recipe that I used to win the 2016 Rensselaer Polytechnic 					Institute Graduate Christian Fellowship Chili cook-off. Take that Ben, with your 				pumpkin spice chili. You what tastes better than my chili, Ben? Victory, Ben. 					Victory. I'm still tweaking this so the end result will probably be 							pretty similar to the award winning version but not exactly.
    }
    
    \ingredients{%
        3 Tbsps & vegetable oil\\
        2 medium & yellow onions\\
        1/2 medium & red bell pepper\\
        1/2 medium & green bell pepper\\
        6 medium & garlic cloves\\
		1/4 cup & chili powder\\
		1 Tbsp & chipotle powder\\
		1 Tbsp & cayenne pepper\\
		4-5 & habanero peppers\\
		1 Tbsp & ground cumin\\
		2 pounds & lean ground beef\\
        1 1/2 tsps & kosher salt\\
        1 28-ounce can & diced tomatoes\\
        1 14-ounce can & tomato sauce\\
        2 15-ounce cans & kidney beans\\
        1/4 cup & jalapenos chopped\\
    }
    
    \preparation{%
        \step Heat the oil in a large frying pan (cast iron skillet) over medium heat until 					shimmering. Add the onions, bell peppers, and habaneros. Season with kosher 					salt. Cook until soft, stirring occasionally, about 8 minutes.
        
        \step Add the garlic, chili powder, cumin, chipotle powder, and cayenne pepper, stir 				to coat vegetables and cook until fragrant, about 1 minute. Add the ground 						beef and measured salt. Brown ground beef and break into small pieces with a 				wooden spoon.
        
        \step Transfer the mixture to the slow cooker, add the diced tomatoes and their 						juices, tomato sauce, and the drained and rinsed kidney beans and stir to 						combine. Cover and cook until chili tickens and the flavors meld, about 8 						hours on low or 6 hours on high.
        
        \step Before serving stir in jalapenos. Serve with chedder cheese, scallions, 							crackers, and sour cream.

    }
    
    \suggestion[Notes]
    {%
        \begin{itemize}
        	\item Chipotle powder and cayenne pepper are not dialed in just yet, include at 						own risk
        	
        	\item The longer you cook this and the thicker it gets the better it tastes. I 							usually cook it for 2 full days and let it rest for 2 nights.
        	
        	\item Tried once with a Brown's Oatmeal Stout. It wasn't bad but it took a lot 							longer to thicken. Personally I preferred it without but if you want to 						stretch it a little further and give it that hipster wow factor add a 							craft stout beer.
        	\item Wear gloves when cutting the hot peppers. For that matter, jalapenos and 							habaneros can be omitted if you're a wimp. I suggest just using less 							though. Just enough to add to the flavor but not enough to burn. It's 							possible.
        \end{itemize}
    }    
\end{recipe}